Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
abstract: turn negative sentences into positive ones
introduction: BDD-style TDD has been pioneerd by RSpec

\begin{quote}\begin{itemize}
    \item
        sol: Should we state that BDD-style TDD has been pioneered by
        RSpec?  By now I think it would be a good idea, that way it
        feels more natural to the reader that we always look at RSpec.

        @mkl: Where would that fit in?
\end{itemize}\end{quote}

In this paper, we explore how to apply BDD to Haskell.
For the purpose of this paper we only focus on the TDD aspect of BDD.

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec~\cite{rspec}, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

>>>>

BDD-style TDD has been pioneered by RSpec~\cite{rspec}.  In this
paper, we explore how to apply the TDD aspect of BDD to Haskell.

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.
